 

### 2023-02-23 paper1.Rmd
Edits to map in Paper 1

lower_block_3_1 <-  fun_lower_block(country = "all",
                                    label = "West \nAfrica",
                                    17.55830898122733, -25.766648641326874,
                                    9.591111921718683, -7.308676054124459,
                                    ratio_h_over_w = 0.69/0.95,
                                    nudge = 1)

@@

                                     rel_heights  = c(0.99,1.72),
                                     rel_widths = c(1,1),
                                     align='h',
                                     nrow= 2,
                                     axis='t')

@@

main_map_lower <- cowplot::plot_grid(lower_block_1,
                                     lower_block_2,
                                     lower_block_3,
                                     lower_block_4,
                                     lower_block_5,
                                     rel_widths = c(3.32,
                                                    3.22,
                                                    1.92,
                                                    2.73,
                                                    1.82),
                                     rel_heights = c(1,1,1,1,1),
                                     align='h', 
                                     ncol=5, 
                                     axis='t')

@@

main_map_combined <- cowplot::plot_grid(main_map_upper,
                                        main_map_lower,
                                        rel_heights = c(5.9, 2.8),
                                        rel_widths = c(1,1),
                                        align='v', 
                                        nrow = 2,
                                        axis='l')
main_map_combined

@@

k = "rate_per_100k"

j = 1

>>>>

lower_block_3_1 <-  fun_lower_block(country = "all",
                                    label = "West \nAfrica",
                                    15.333951130672313, -20.03959428947879,
                                    8.941590169786489, -7.402043441729575,
                                    ratio_h_over_w = 0.69/0.95,
                                    nudge = 1)

@@

                                     rel_heights  = c(1.1,1.72),
                                     rel_widths = c(1.1,1),
                                     align='h',
                                     nrow= 2,
                                     axis='t')

@@

main_map_lower <- cowplot::plot_grid(lower_block_1,
                                     lower_block_2,
                                     lower_block_3,
                                     lower_block_4,
                                     lower_block_5,
                                     rel_widths = c(3.32,
                                                    3.22,
                                                    2,
                                                    2.73,
                                                    1.83),
                                     rel_heights = c(1,1,1,1,1),
                                     align='h', 
                                     ncol=5, 
                                     axis='t')

@@

main_map_combined <- cowplot::plot_grid(main_map_upper,
                                        main_map_lower,
                                        rel_heights = c(5.9, 
                                                        2.7),
                                        rel_widths = c(1.2,1),
                                        align='v', 
                                        nrow = 2,
                                        axis='l')
main_map_combined

@@

data_temporary <- data_rev_map %>% 
  filter(estimate_id %in%  c(1,2,4)) %>%
  st_drop_geometry()

world_map <- ne_countries(scale = "large", returnclass = "sf")
# world <- ne_countries(scale = "medium", returnclass = "sf")
world_map$iso_code <- world_map$gu_a3
world_map$iso_code[world_map$adm0_a3 == "SDS"] <- "SSD"

data_rev_map <- left_join(world_map, data_temporary, by = "iso_code")

k = "rate_per_100k"
j = 1
